Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-01-22 paper/paper.Rmd
removed figures and tables
minor progress on methods

Where the shape parameter $a$ determines the tail of the distribution, and $b$ is the scale parameter. It is worth mentioning that the standard parameterization of the Weibull in 'R' is different from the parameterization used in Morales and Carlo  [-@morales_effects_2006], where the shape parameter $a = \nu$ remains the same, but the scale parameter is defined as $\kappa = b^{-\nu}$, giving a density distribution function of $W(r)= \kappa\nu r^{\nu-1} exp[-{\kappa r}^\nu]$. 
<!-- Here, we report the scale parameter following the alternative parameterization, but the original values returned after fitting the Weibull distribution using R can be found in the Supplementary Table 1.  -->
Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu <1$ the tail shows fast-decay, and when $\nu>1$ we can see a fat-tailed distribution (Fig 3.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit (Supplementary information).

>>>>

Where the shape parameter $a$ determines the tail of the distribution, and $b$ is the scale parameter. It is worth mentioning that the standard parameterization of the Weibull distribution in 'R' is different from the parameterization used in Morales and Carlo  [-@morales_effects_2006], where the shape parameter $a = \nu$ remains the same, but the scale parameter is defined as $\kappa = b^{-\nu}$, giving a density distribution function of $W(r)= \kappa\nu r^{\nu-1} exp[-{\kappa r}^\nu]$. 
<!-- Here, we report the scale parameter following the alternative parameterization, but the original values returned after fitting the Weibull distribution using R can be found in the Supplementary Table 1.  -->
Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu <1$ the tail shows fast-decay, and when $\nu>1$ we can see a fat-tailed distribution (Fig 3.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit.

Given our interest in the tail-end of the seed dispersal kernels and our focus on the occurrence of long-distance events, we decided to use an extreme value theory approach and fit a Generalized Pareto distribution to the dispersal distances above the 500m threshold established.
